Computer Science House Constitution

### 2021-11-21 constitution.tex
Added eboard abilityto initiate second process

% BY-LAW IV - OPERATIONS OF THE EVALUATIONS DIRECTORSHIP
\asubsection{Operations of the Evaluations Directorship}
\asubsubsection{The Introductory Process}
The Introductory Process is designed to provide an easy means for Introductory Members to meet existing House members, learn House history, demonstrate their involvement potential to House, and allow existing House members to evaluate them for Active Membership.
\asubsubsubsection{The Evaluation Period}
The Process will occur either once or twice per semester, at the discretion of the Evaluations Director, and will last for six (6) weeks.
The Process shall be initiated by the Evaluations Director during either the first or second week of each semester.
The Executive Board may hold a closed ballot Simple Majority vote to extend the Introductory Process or the Introductory Packet.
If an Introductory Process is extended, the Introductory Evaluation shall occur at the termination of the extended Process, which may be outside of the period defined in \ref{Introductory Evaluation}.
If deemed necessary by the Evaluations Director, the second intro process must begin within nine (9) days of the first process ending.
\asubsubsubsection{The Introductory Packet}
Each Introductory Process participant, after the first week, is given two (2) weeks to return a document that should contain a signature from all Active members, all Introductory Resident members, and ten (10) of any combination of the following:
\begin{itemize}
	\item Alumni members
	\item Honorary members
	\item Advisory members
\end{itemize}
At the discretion of the Evaluations Director, any Introductory Packet may be extended to accommodate extenuating circumstances.
\asubsubsubsection{Expectations of an Introductory Member}
Before the end of the Process, an Introductory Member is expected to:
\begin{itemize}
\item Attend all House meetings during the process
\item Complete the Introductory Packet
\item Attend at least one House directorship meeting for each week of the process (including permanent and Ad Hoc directorship meetings)
\item Attend at least one House social event during the process
\item Attend at least two seminars relating to computing or electronics
\item Sign a copy of the Membership Agreement describing a House Member’s responsibilities and expectations
\end{itemize}

>>>>

% BY-LAW IV - OPERATIONS OF THE EVALUATIONS DIRECTORSHIP
\asubsection{Operations of the Evaluations Directorship}
\asubsubsection{The Introductory Process}
The Introductory Process is designed to provide an easy means for Introductory Members to meet existing House members, learn House history, demonstrate their involvement potential to House, and allow existing House members to evaluate them for Active Membership.
\asubsubsubsection{The Evaluation Period}
The Process will occur either once or twice per semester, at the discretion of the Evaluations Director, or by an Executive Board simple majority vote, and will last for six (6) weeks.
The Process shall be initiated by the Evaluations Director during either the first or second week of each semester.
The Executive Board may hold a closed ballot Simple Majority vote to extend the Introductory Process or the Introductory Packet.
If an Introductory Process is extended, the Introductory Evaluation shall occur at the termination of the extended Process, which may be outside of the period defined in \ref{Introductory Evaluation}.
If deemed necessary by the Evaluations Director, the second intro process must begin within nine (9) days of the first process ending.
\asubsubsubsection{The Introductory Packet}
Each Introductory Process participant, after the first week, is given two (2) weeks to return a document that should contain a signature from all Active members, all Introductory Resident members, and ten (10) of any combination of the following:
\begin{itemize}
	\item Alumni members
	\item Honorary members
	\item Advisory members
\end{itemize}
At the discretion of the Evaluations Director, any Introductory Packet may be extended to accommodate extenuating circumstances.
\asubsubsubsection{Expectations of an Introductory Member}
Before the end of the Process, an Introductory Member is expected to:
\begin{itemize}
\item Attend all House meetings during the process
\item Complete the Introductory Packet
\item Attend at least one House directorship meeting for each week of the process (including permanent and Ad Hoc directorship meetings)
\item Attend at least one House social event during the process
\item Attend at least two seminars relating to computing or electronics
\item Sign a copy of the Membership Agreement describing a House Member’s responsibilities and expectations
\end{itemize}
